The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Spaces for Headings

###Research Question  
Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?

###Research Justification
When it comes to public budgeting for education policies, the decision process often does not appear to be rational. That is, it does not seem to take into account the return on investment that should be expected in the long run. Despite this, many claims have been made in the entrepreneurship literature that start-up activities at a country-level are affected by factors other than structural and economic, including cultural and educational. However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.

@@

###Literature Review

@@

####Estimation Strategy  
The estimation strategy will consist of using cross-sectional data about France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.

@@

###Necessary Concepts  
1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.

@@

###References

>>>>

### Research Question  
Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?

### Research Justification
When it comes to public budgeting for education policies, the decision process often does not appear to be rational. That is, it does not seem to take into account the return on investment that should be expected in the long run. Despite this, many claims have been made in the entrepreneurship literature that start-up activities at a country-level are affected by factors other than structural and economic, including cultural and educational. However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.

@@

### Literature Review

@@

#### Estimation Strategy  
The estimation strategy will consist of using cross-sectional data about France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.

@@

### Necessary Concepts  
1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.

@@

### References
